### 2023-06-19 manuscript.tex
add placeholder [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/e52fbde2994a307c76a8d2ec15346bfec89f46a9.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/e52fbde2994a307c76a8d2ec15346bfec89f46a9/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/5314901344

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/b6e8bff54a82660f8e7c4a55245cf69efa6f4599/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/b6e8bff54a82660f8e7c4a55245cf69efa6f4599}{MMV-Lab/im2im-paper@b6e8bff}
on April 18, 2023.

@@

@@

Finally, beyond \emph{MMV\_Im2Im}, we hope to build develop similar package for other problems (without re-inventing wheels). For example, as we mentioned in the instance segmentation application, Mask-RCNN type models are also very powerful instance segmentation methods and, in theory, can also be generalized beyond 2D images. However, Mask-RCNN would fit more to a detection framework, instead of image-to-image transformation. It will be supported in our \emph{MMV\_NDet} (NDet = N-dimensional detection) package, currently under development.

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/e52fbde2994a307c76a8d2ec15346bfec89f46a9/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/e52fbde2994a307c76a8d2ec15346bfec89f46a9}{MMV-Lab/im2im-paper@e52fbde}
on June 19, 2023.

@@

\hypertarget{microscopy-images-with-temporal-information}{%
\subsubsection{Microscopy images with temporal information}\label{microscopy-images-with-temporal-information}}

\hypertarget{further-works}{%
\subsubsection{Further works}\label{further-works}}

@@

Another type of microscopy image analysis problem related to image to image transformation is image registration, where we learn how to transform the ``floating'' image spatially so that it is optimally aligned with the refernece image in the physcially space. Elastix \ldots{} image-to-image transformation without well aligned training data.

Beyond \emph{MMV\_Im2Im}, we hope to build develop similar package for other problems (without re-inventing wheels). For example, as we mentioned in the instance segmentation application, Mask-RCNN type models are also very powerful instance segmentation methods and, in theory, can also be generalized beyond 2D images. However, Mask-RCNN would fit more to a detection framework, instead of image-to-image transformation. It will be supported in our \emph{MMV\_NDet} (NDet = N-dimensional detection) package, currently under development.
